%
% File acl2020.tex
%
%% Based on the style files for ACL 2020, which were
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{color, colortbl}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[latin1]{inputenc}
\usepackage{latexsym}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{times}
\usepackage{url}
\usepackage{xcolor}
\usepackage{xspace}

\renewcommand{\UrlFont}{\ttfamily\small}

%\usepackage{microtype}

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
\newcommand{\gbt}[1]{\textcolor{orange}{\emph{//gbt: #1//}}}
\newcommand{\cs}[1]{\textcolor{green!60!black}{\emph{//cs: #1//}}}
\newcommand{\mw}[1]{\textcolor{orange!60!black}{\emph{//mw: #1//}}}

% To streamline frequently used terms:
\newcommand{\langvis}{language\ \&\ vision\xspace}
\newcommand{\lv}{L\&V\xspace}
\newcommand{\mn}{ManyNames\xspace}
\newcommand{\mnshort}{MN\xspace}
\newcommand{\vg}{VisualGenome\xspace}
\newcommand{\ra}{$\rightarrow$}
\newcommand{\sameobject}{SameObject\xspace}
\newcommand{\cluster}{Cluster\xspace}

\newcommand{\cat}[1]{\textsc{#1}}
\newcommand{\name}[1]{\textsl{#1}}

% Terms that need to be replaced throughout the paper by more appropriate ones:
\newcommand{\arbitrary}{arbitrary\xspace}
\newcommand{\categories}{classes\xspace}
\newcommand{\category}{class\xspace}

\title{From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
Object detection and image classification models from Computer Vision are typically trained towards predicting labels of objects. 
Our goal is to extend such models to entry-level naming, where the task is to predict the natural name of an object that most humans would choose, instead of an \arbitrary name chosen by at best a few annotators. 
Based on large-scale, thoroughly verified object naming data from many annotators, we conduct an extensive analysis of the ability of object detection and classification models to account for entry-level object naming.
We show that standard object classification models ``spontaneously'' learn good entry-level names and perform better
on predicting entry-level than \arbitrary names, despite being trained on the latter, and that we can use transfer learning to train entry-level classifiers on the naming data. 
%Our analyses also demonstrate the challenges of collecting data of language phenomena that serves as a proxy for real-world situations in which the phenomenon of interest occurs.
%and systematically vary their training vocabulary. \cs{no diffs here with our setup of entry-levels only}
\end{abstract}

\section{Introduction}
\label{sec:intro}
\input{introduction}

\section{Related Work}
\label{sec:related}
\input{related}

\section{Adequacy and Errors in ManyNames}
\label{sec:manynames}
%\cs{to add: footnote saying that the \mn data will be published upon acceptance of the paper.}
\input{manynames}

\section{Predicting Entry-Level Names}
\label{sec:experiments}
\input{experiments}

\section{Analysis of Model Naming Behavior}
\label{sec:analysis}
\input{analysis}

\section{Conclusions}
\label{sec:conclusions}
In this paper, we have investigated instance-level entry-level naming of objects in images.
To the best of our knowledge, our work is the first to investigate entry-level naming on such a large-scale but thorougly verified empirical basis, 
as opposed to previous works that mostly adopted a class-level and/or strictly taxonomic view of naming.
For models in \lv, the complexity of human naming data we observed brings up an important question: how should a naming models best fine-tune and calibrate the \textit{vocabulary} of object detection and classification models from Computer Vision, in order to capture natural naming behavior?
We showed that the best way to achieve this is to first retrain an object detector on a large set of \arbitrary names and then fine-tune via transfer learning to entry-level names. 
In future work, we plan to develop this approach further and assess, e.g., how well the learned naming vocabulary generalizes for other, external datasets.
We also showed that naming data elicited for boxed objects comes with certain challenges, which have to be considered during evaluation (and potentially during modeling). 
%Bounding boxes are not always clear enough pointers to objects, and at the same time there is no clear line between other object mistakes (\textit{batter-helmet}), referential disagreements (\textit{bed-sleeping bag}, when the two visually overlap in the image), and valid alternatives (\textit{carpet-floor} can be a metonymy).
%Future work will need to address these challenges. 

%\bibliography{BLA}
%\bibliographystyle{acl_natbib}

%\appendix
%
% \section{Appendices}\newcommand{sameobject}
% \label{sec:appendix}
% \iffalse
% Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper.
% Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
% Upon acceptance, the appendices come after the references, as shown here.

% \paragraph{\LaTeX-specific details:}
% Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
% \fi

% \section{Supplemental Material}
% \label{sec:supplemental}
% \iffalse
% Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
% Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.
% \fi

\bibliographystyle{acl_natbib}
\bibliography{naming}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "acl2020_main"
%%% End:
